Tor's Usability for Censorship Circumvention

### 2015-10-05 paper/circumvention-experiment.tex
moved explaining purpose of tasks to experiment flow
hashed out deliverables
finished deliverables

\noindent {\bfseries Censorship Environment Simulation}

We plan to simulate three censorship environments.
They are informed by our experience with pluggable transports
and knowledge of commonly seen censorship techniques.
They are not meant perfectly to replicate the network environment
in any particular country; rather, they are abstract simulations
that are nevertheless inspired by reality.

@@

In certain real censorship environment and our most 
prohibitive simulated censorship environments, only some of 
Tor's pluggable transports work in censorship environments
where others do not. Some of them require additional information
(like bridge addresses) before they work. Currently, we do not 
have a way to target test specific transports. However, we 
do ask why participants chose a specific pluggable 
transport in our exit survey to gain some insight.

@@

% measure how an average user might configure Tor in various circumention settings
% test improvement and alternate configuration 
% make changes!

>>>>

\noindent {\bfseries Censorship Environment Simulation} 
We plan to simulate three censorship environments.
They are informed by our experience with pluggable transports
and knowledge of commonly seen censorship techniques.
They are not meant perfectly to replicate the network environment
in any particular country; rather, they are abstract simulations
that are nevertheless inspired by reality.

@@

In certain real censorship environment and our most 
prohibitive simulated censorship environments, only some of 
Tor's pluggable transports work in censorship environments
where others do not. Some of them require additional information
(like bridge addresses) before they work. Currently, we do not 
have a way to target test specific transports. However, we 
do ask why participants chose a specific pluggable 
transport in our exit survey to gain some insight.\\

@@

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item {\bfseries Test the Tor configuration interface} We will perform the largest-scale user study 
of Tor to date, measuring how users configure Tor in three different adversarial settings. 
\item {\bfseries Test an improved configuration interface} With the measurements collected
from testing the interface as-is, Nathan will be designing ways to improve the interface to minimize
time taken, paths taken, and error states reached.
\item {\bfseries Test an alternative configuration interface} A Tor developer has offered
to design a mock-up interface for an alternative configuration interface which will
greatly automate the process. There are tradeoffs between ease of use and transparency
of the system's, and ethical considerations with loggable errors resulting from automated configuration. 
\item {\bfseries Push changes} We have the support of Tor developers
to improve this interface. Additionally, since the configuration interface does not require 
any changes to the Tor Browser functionality, improvements to the interface will
be easy to deploy. 
\end{itemize}
